---
title: "Lab 00 - Hello IDS!"
author: "Lucy"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Lucy", "Joel", "Zazzie", "Gabriel", 
           "Alex", "Jin"),
  github_username = c("roydsle", "joelhanloned", "zarinakjellberg", "gamgow", "alexjdlr", "jin2226"), 
  colour = c("maroon3", "pink", "hotpink1", "hotpink", 
             "maroon2", "violet"),
  hobby = c("disney +", "drums", "netball", "jazz trumpet", 
            "cooking", "reading"),
  favourite_number = c(7, 2, 2, 4, 10, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = hobby, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows, per hobby, the favourite number and colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "hobby", 
          y = "favourite number",
          title = "data practice")
```

labels 

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
